---
title: "ODD Assignment Part2"
author: "Muharrem Çakır"
date: "23 Kasım 2018"
output: html_document
---
## Install Package
In week 2 everyone was studied just one period of ODD data. Now we combine all data and   we can study all periods to make deep analyses.
First of all we have to install some package that will be  used below.
```{r}
install.packages("tidyverse", repos = "https://cran.r-project.org")
install.packages("formattable", repos = "https://cran.r-project.org")

library(tidyverse)
library(dplyr)
library(formattable)
library(ggplot2)
```

## Download Data
Here we read data from github repository and assign it to a dataframe.

```{r}
githubURL <- ("https://github.com/MEF-BDA503/pj18-muharremcakir81/blob/master/Week4/car_data_aggregate.rds?raw=true")
All_data<- readRDS(url(githubURL))
head(All_data)
```

## DATA UNDERSTANDING & CLEANING CONTROL

Comment: when we grouped data by brandname we saw that some rows were appear like 'TOPLAM' or starts with 'ODD...'
We cleaned some rows which's brand_name variable include  'TOPLAM' and "ODD....." value.

```{r}
Control_Data <- All_data%>%
  group_by (brand_name)%>%
  summarize(count=n())


Cleaned_data <-All_data%>%
  filter(brand_name != "TOPLAM:")%>%
  filter(!grepl(pattern ="ODD", brand_name))

#View(Cleaned_data)

```

## DATA MODIFY
we just select brand_name and total Sales in 201809, 201808 and 201709  periods from all data respectively and assigng each period to diffent dataframe.
Soma Data manipulation and enrichment operations are done to make comparison between  201809, 201808 and 201709  periods.
So that we can see the increase rate for each brand. 

```{r}

total_201809 <- Cleaned_data %>%
            filter (year == 2018, month == 9) %>%
            select (brand_name,total_total) %>%
            rename(Total_201809 = total_total)
#View(total_201809)

#I just select brand_name and total Sales in 201808 period from all data. 

total_201808 <- Cleaned_data %>%
  filter (year == 2018, month == 8) %>%
  select (brand_name,total_total) %>%
  rename(Total_201808 = total_total)
#View(total_201808)

#I just select brand_name and total Sales in 201709 period from all data. 
total_201709 <- Cleaned_data %>%
  filter (year == 2017, month == 9) %>%
  select (brand_name,total_total) %>%
  rename(Total_201709 = total_total)
#View(total_201709)

#I just select brand_name and sum total sales of  first 9 months periods in 2018 from all data. 

total_2018_YTD <- Cleaned_data %>%
  filter (year == 2018) %>%
  group_by (brand_name)%>%
  summarize(Total_2018_YTD = sum(total_total)) %>%
  select (brand_name,Total_2018_YTD)

#View(total_2018_YTD)

#I just select brand_name and sum total sales of  first 9 months periods in 2017 from all data. 

total_2017_YTD <- Cleaned_data %>%
  filter (year == 2017,month <= 9) %>%
  group_by (brand_name)%>%
  summarize(Total_2017_YTD = sum(total_total)) %>%
  select (brand_name,Total_2017_YTD)

#View(total_2017_YTD)

```
##JOIN ALL TEMP DATA SET 
After join all temp dataframe each other replaced  NA values to 0 in all variable.
```{r}
Denormalize_data <- total_201709 %>%
  full_join(total_201808, by="brand_name")  %>%
  full_join(total_201809, by="brand_name") %>%
  full_join(total_2017_YTD, by="brand_name") %>%
  full_join(total_2018_YTD, by="brand_name")

Denormalize_data <- mutate_all(Denormalize_data,funs(replace(., is.na(.), 0)))
#View(Denormalize_data)
```
##CALCULATE NEW VARIABLE
```{r}

Brand_Increase_Rate <- Denormalize_data%>%
  mutate(CM_PM_Total_Rate = round((ifelse (Total_201808  == 0 , NA, #(Total_201809 - Total_201808) *100,
                                    (Total_201809 - Total_201808) / Total_201808 *100)),1)) %>%
  mutate(CM_PYM_Total_Rate = round((ifelse (Total_201709  == 0 ,NA, #(Total_201809 - Total_201709) *100,
                                     (Total_201809 - Total_201709) / Total_201709 *100)),1)) %>%
  mutate(YTD_PYTD_Total_Rate = round((ifelse (Total_2017_YTD  == 0 ,(Total_2018_YTD - Total_2017_YTD) *100,
                                     (Total_2018_YTD - Total_2017_YTD) / Total_2017_YTD *100)),1)) %>%
  mutate(Percentage_2018_YTD = round((Total_2018_YTD / sum(Total_2018_YTD) *100),2), Percentage_2017_YTD = round((Total_2017_YTD / sum(Total_2017_YTD) *100),2)) %>%
  select(brand_name,Total_201809,Total_201808,Total_201709,Total_2018_YTD,Percentage_2018_YTD,Total_2017_YTD,Percentage_2017_YTD,
         CM_PM_Total_Rate,CM_PYM_Total_Rate,YTD_PYTD_Total_Rate)%>%
  arrange(desc(Percentage_2018_YTD))

```
##FORMAT TABLE
To recognize the descreasing the sales amount from 2017 to 2018 and to see which brands are sold above the avearage we formatted table...
It's clear that most of all brands' salling is decrease from 2017 to 2018. 
**VOLKWAGEN is sold %8.14 of all cars in 2017 and sold %10.9 0f all data in 2018.So Volkwagen's selling perfomance is increasing. Also it's able to increase  total selling in 9 months in 2018 across in 9 months in 2017 (%5,4) 
**Also VOLVO' is very 's performance is very impressive. its selling amount is increased %35.1 percentage in 9 months in 2018.
```{r}

color <- formatter("span", style = x ~ style(color = ifelse(x > 0, "green",ifelse(x < 0, "red", "black"))))


avg_bold <- formatter("span",  style = x ~ style("font-weight" = ifelse(x > mean(x), "bold", NA)))


formattable(Brand_Increase_Rate, 
            list(Total_2018_YTD = avg_bold,
                 Total_2017_YTD = avg_bold, 
                 CM_PM_Total_Rate = color, 
                 CM_PYM_Total_Rate = color,
                 YTD_PYTD_Total_Rate = color))
```

##Finaly there are two grafic analyses here. We take 4 brands (RENAUT,FORD,VOLKSWAGEN,FIAT,HYUNDAI) that achive %50 of total car's saling. 

```{r}

trend_analyses <- Cleaned_data %>%
  filter (brand_name %in% c("RENAULT","FORD","VOLKSWAGEN","FIAT","HYUNDAI")  & year == 2018)%>%
  select(brand_name,month,total_total)
#View(trend_analyses)

ggplot(trend_analyses,aes(x=month,y=total_total ,color = brand_name)) +geom_line()

brand_analyses <- Cleaned_data %>%
  filter (brand_name %in% c("RENAULT","FORD","VOLKSWAGEN","FIAT","HYUNDAI")  & year== 2018)%>%
  group_by(brand_name) %>%
  summarize(total_by_brand = sum(total_total))%>%
  select(brand_name,total_by_brand)
#View(brand_analyses)

ggplot(brand_analyses,aes(x=brand_name,y=total_by_brand)) +geom_col()
```


